Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-11 paper/galsize_paper.tex
Added paragraph discussing potential importance of halo definition

>>>>

In any model where galaxy $\rhalf$ co-evolves with halo $\rvir,$ the choice of halo boundary definition necessarily impacts the model prediction. Since the clustering of halos has non-trivial dependence upon halo definition \citep{villarreal_etal17}, then measurements of galaxy clustering may be able to observationally distinguish a particular halo boundary that is most closely connected to galaxy size. The redshift evolution of the relationship between $\mhalo$ and $\rvir$ also varies with halo definition, and so measurements of $\rhalf-$dependent clustering across redshift may provide a further observational handle on the halo radius definition that best predicts galaxy size.
